Introduction to Causal Inference Models

### 2017-07-31 msm_introduction.Rmd
figured out g-formula est for tv model

>>>>

Trying to replicate example in sas code.
```{r}
y_mod <- glm(Y ~ A1 + Z1 + A0 + A1*A0, data = td_sim_data, family = "gaussian")
z1_mod <- glm(Z1 ~ A0, data = td_sim_data, family = "binomial"(link="logit"))
a1_mod <- glm(A1 ~ Z1, data = td_sim_data, family = "binomial"(link="logit"))

# natural course estimate
nc_mu <- mean(predict(y_mod, newdata = td_sim_data, type = "response"))

# fully exposed
z1_pr <- mean(predict(z1_mod, newdata = mutate(td_sim_data, A0 = 1), type = "response"))
# simulate vector of new Z1 values accounting for prior A0
z1_vec <- ifelse(rbernoulli(n = nrow(td_sim_data), z1_pr)==T,1,0)
# update a1 
a1_pr <- mean(predict(a1_mod, newdata = as.tibble(z1_vec), type = "response"))
# simulate new a1 given z1 under a0 estimate
a1_vec <- ifelse(rbernoulli(n = nrow(td_sim_data), a1_pr)==T,1,0)

all_exposed <- mean(predict(y_mod, newdata = mutate(td_sim_data, A1 = 1, A0 = 1, Z1 = z1_vec),
                type = "response"))

head(mutate(td_sim_data, A1 = 1, A0 = 1))

MSModelR::g.formula
```
